Variants on the Flight and Maintenance Planning problem

### 2019-04-19 latex/notes/model/model.tex
changes on model.tex

\setlength{\parskip}{2ex} \pagestyle{myheadings}
% \markright{\hspace*{3.8cm} \textit{MOSIM18 - June 27-29, 2018 - Toulouse - France}}

@@

        \begin{tabular}{p{15mm}p{125mm}p{15mm}}
            $PA^{Clust}_s$   & unit penalty for violating serviceability constraint in slot $s$. & \\
            $PH^{Clust}_s$   & unit penalty for violating sustainability constraint in slot $s$. & \\
        \end{tabular}

@@

    \begin{tabular}{p{8mm}p{147mm}}
        $h_{in}$  &  Continuous, positive. Sum of the accumulated monthly consumption in flight hours for aircraft $i \in I$ for maintenance cycle $n$. \\
        $e^{AClust}_{kts}$ & Continuous, positive. Elastic variable for serviceability constraint. \\
        $e^{HClust}_{kts}$ & Continuous, positive. Elastic variable for sustainability constraint. \\
    \end{tabular}

@@

    Objective (\ref{eq:objective1}) minimizes the number of checks while at the same time maximizing the monthly total flight hours potential of the fleet.

    \begin{align}
        & \text{Min}\; 
        \sum_{\substack{i \in \mathcal{I}, \\ 
            t_1 \in \mathcal{T}^{M_{Init}}_i, \\ 
            t_2 \in \mathcal{T}^M_{t_1} - |\mathcal{T}|}
            }  
            m_{it_1t_2} \times H^{max} 
        + \sum_{k \in \mathcal{K}, t \in \mathcal{T}, s \in \mathcal{S}} PA^{Clust}_s e^{AClust}_{kts} 
        + \sum_{k \in \mathcal{K}, n \in \mathcal{N}, s \in \mathcal{S}} PH^{Clust}_s e^{HClust}_{kns}
        \label{eq:objective1}
    \end{align}

    The first term counts all the remaining flight hours given to aircraft following checks and the second term quantifies the amount of remaining flight hours for all aircraft at each period. These two objectives have the same units, can be easily compared and ensure the aircraft are used in the most efficient way.

    The following constraints are used in the model:
    \begin{align}
        % maximum capacity1:
        & \sum_{\substack{i \in \mathcal{I}, \\ (t_1, t_2) \in \mathcal{T}\mathcal{T}\mathcal{T}_{t}}} m_{it_1t_2} + N_t \leq C^{max}
          & t \in \mathcal{T} \label{eq:capacity1}\\
        % min assignments:
        & \sum_{\substack{i \in \mathcal{IJ}_j, \\ (t_1, t_2) \in \mathcal{T}\mathcal{T}\mathcal{J}_{jt}}} a_{ijt_1t_2} \geq R_j
                & j \in \mathcal{J}, t \in \mathcal{TJ}_j  \label{eq:missionres}\\
        % just doing one thing at any given time:
        & \sum_{\substack{(t_1, t_2) \in \\ \mathcal{T}\mathcal{T}\mathcal{T}_{t}}} m_{it_1t_2} + \sum_{\substack{j \in \\ \mathcal{JT}_t \cap \mathcal{JI}_i}} \sum_{\substack{(t_1, t_2) \in \\ \mathcal{T}\mathcal{T}\mathcal{J}_{jt}}} a_{ijt_1t_2} \leq 1 
                & t \in \mathcal{T}, i \in \mathcal{I} \label{eq:state}
    \end{align}

@@

    \begin{align}
       & \sum_{\substack{i \in \mathcal{IK}_k, \\ (t_1, t_2) \in \mathcal{T}\mathcal{T}\mathcal{T}_{t}}} m_{it_1t_2} + N^{Clust}_{kt} \leq A^{Clust}_{kt} + \sum_{s \in \mathcal{S}} e^{AClust}_{kts}
        &k \in \mathcal{K}, t \in \mathcal{T} \label{eq:serviceability-cluster}\\
       & \sum_{i \in \mathcal{IK}_k} h_{in} \leq |{IK}_k| H^{Clust}_{kn} + \sum_{s \in \mathcal{S}} e^{HClust}_{kns}
        &k \in \mathcal{K}, n \in \mathcal{N} \label{eq:sustainability-cluster}
    \end{align}

>>>>

\setlength{\parskip}{2ex} \pagestyle{myheadings}

@@

        \begin{tabular}{p{15mm}p{125mm}p{15mm}}
            $PA_s$   & unit penalty for violating serviceability constraint in slot $s$. & \\
            $PH_s$   & unit penalty for violating sustainability constraint in slot $s$. & \\
            $PC_s$           & unit penalty for violating capacity constraint in slot $s$. & \\
        \end{tabular}

@@

    \begin{tabular}{p{8mm}p{147mm}}
        $h_{in}$  &  Continuous, positive. Sum of the accumulated monthly consumption in flight hours for aircraft $i \in I$ for maintenance cycle $n$. \\
        $e^{A}_{kts}$ & Continuous, positive. Elastic variable for serviceability constraint (\ref{eq:serviceability-cluster}). \\
        $e^{H}_{kts}$ & Continuous, positive. Elastic variable for sustainability constraint (\ref{eq:sustainability-cluster}). \\
        $e^{C}_{ts}$ & Continuous, positive. Elastic variable for capacity constraint (\ref{eq:capacity1}). \\
    \end{tabular}

@@

    Objective (\ref{eq:objective1}) minimizes the deviations number of checks while at the same time maximizing the monthly total flight hours potential of the fleet.

    \begin{align}
        & \text{Min}\; 
        \sum_{\substack{
                k \in \mathcal{K}, \\ t \in \mathcal{T}, \\ s \in \mathcal{S}
                }
            } PA_s e^{A}_{kts} 
        + \sum_{\substack{
                k \in \mathcal{K}, \\ n \in \mathcal{N}, \\ s \in \mathcal{S}
                } 
            } PH_s e^{H}_{kns}
        + \sum_{t \in \mathcal{T}, s \in \mathcal{S}} PC_s e^{C}_{ts}
        \label{eq:objective1}
    \end{align}

    The following constraints are used in the model:
    \begin{align}
        % maximum capacity1:
        & \sum_{\substack{i \in \mathcal{I}, \\ (t_1, t_2) \in \mathcal{T}\mathcal{T}\mathcal{T}_{t}}} m_{it_1t_2} + N_t \leq C^{max} + \sum_{s \in \mathcal{S}} e^{C}_{ts}
                & t \in \mathcal{T} \label{eq:capacity1}\\
        % min assignments:
        & \sum_{\substack{i \in \mathcal{IJ}_j, \\ (t_1, t_2) \in \mathcal{T}\mathcal{T}\mathcal{J}_{jt}}} a_{ijt_1t_2} \geq R_j
                & j \in \mathcal{J}, t \in \mathcal{TJ}_j  \label{eq:missionres}\\
        % just doing one thing at any given time:
        & \sum_{\substack{(t_1, t_2) \in \\ \mathcal{T}\mathcal{T}\mathcal{T}_{t}}} m_{it_1t_2} + \sum_{\substack{j \in \\ \mathcal{JT}_t \cap \mathcal{JI}_i}} \sum_{\substack{(t_1, t_2) \in \\ \mathcal{T}\mathcal{T}\mathcal{J}_{jt}}} a_{ijt_1t_2} \leq 1 
                & t \in \mathcal{T}, i \in \mathcal{I} \label{eq:state}
    \end{align}

@@

    \begin{align}
       & \sum_{\substack{i \in \mathcal{IK}_k, \\ (t_1, t_2) \in \mathcal{T}\mathcal{T}\mathcal{T}_{t}}} m_{it_1t_2} + N^{Clust}_{kt} \leq A^{Clust}_{kt} + \sum_{s \in \mathcal{S}} e^{A}_{kts}
        &k \in \mathcal{K}, t \in \mathcal{T} \label{eq:serviceability-cluster}\\
       & \sum_{i \in \mathcal{IK}_k} h_{in} \leq |{IK}_k| H^{Clust}_{kn} + \sum_{s \in \mathcal{S}} e^{H}_{kns}
        &k \in \mathcal{K}, n \in \mathcal{N} \label{eq:sustainability-cluster}
    \end{align}
